|

### 2019-06-03 manuscript/article/article.Rmd
update R code manuscript

Users can download the data as an Excel spreadsheet (`.xlsx`) or as a comma-separated values text file (`.csv`).  We have also created an `R` package called `pinochet` which includes the dataset in both formats plus the data codebook. The files follow the principles of "tidy data", where each column represents one variable and each row is one case [@wickham2014tidy]. The `pinochet` package is available for download on the Comprehensive R Archive Network (CRAN) and at <http://github.com/danilofreire/pinochet>. To make the data accessible, our GitHub repository has detailed installation instructions for users new to `R`.

@@

```{r sample-obs, echo=FALSE, warning=FALSE, message=FALSE,cache=TRUE}
if (!require("kableExtra")) {
        install.packages("kableExtra")
}
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
load("/Users/politicaltheory/Documents/github/pinochet/data/pinochet.RData")
kable(t(pinochet[12, c(1:4,7:22,24:37)]), "latex", caption = "Sample event from the dataset (selected variables)", col.names = c("Value"), booktabs = T) %>%
  kable_styling(position ="center", latex_options = "hold_position")
```

@@

```{r time-trend-perpetrators, echo=FALSE, fig.align='center', fig.height=4, fig.width=5, warning=FALSE, message=FALSE, fig.cap='Violence perpetrators in the Pinochet regime, 1973-1990'}
# Load requied packages
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
if (!require("lubridate")) {
        install.packages("lubridate")
}
# Plot
pinochet %>% 
  select(c(perpetrator_affiliation, start_date_monthly)) %>%
  mutate(Year = year(start_date_monthly)) %>%
  filter(!is.na(perpetrator_affiliation)) %>% 
  filter(!is.na(Year)) %>%
  filter(Year >= 1975) %>%
  group_by(perpetrator_affiliation, Year) %>%
  summarise(no_rows = length(perpetrator_affiliation)) %>%
  ggplot(aes(x = Year, y = no_rows, colour = perpetrator_affiliation)) +
  viridis::scale_color_viridis(discrete = TRUE,
                               end = 0.5, direction = -1) + 
  geom_line() +
  theme_minimal() +
  labs(x = NULL, y = NULL, title = "Violence Perpetrators", 
       subtitle = "Pinochet Regime, 1975-1990") +
  scale_x_continuous(breaks = c(1975, 1980, 1985, 1990)) +
  facet_grid(perpetrator_affiliation ~ ., scales = "fixed") + 
  theme(legend.position = "bottom") + 
  theme(legend.title=element_blank())
```

>>>>

Users can download the data as an Excel spreadsheet (`.xlsx`) or as a comma-separated values text file (`.csv`).  We have also created an `R` package called `pinochet` which includes the dataset in both formats plus the data codebook. The files follow the principles of "tidy data", where each column represents one variable and each row is one case [@wickham2014tidy]. The `pinochet` package is available for download on the [Comprehensive R Archive Network (CRAN)](https://cran.r-project.org/package=pinochet) and at <http://github.com/danilofreire/pinochet>. To make the data accessible, our GitHub repository has detailed installation instructions for users new to `R`.

@@

```{r sample-obs, echo=FALSE, warning=FALSE, message=FALSE}
if (!require("kableExtra")) {
        install.packages("kableExtra")
}
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
if (!require("pinochet")) {
        install.packages("pinochet")
}
kable(t(pinochet[12, c(1:4,7:22,24:37)]), "latex", caption = "Sample event from the dataset (selected variables)", col.names = c("Value"), booktabs = T) %>%
  kable_styling(position ="center", latex_options = "hold_position")
```

@@

```{r time-trend-perpetrators, echo=FALSE, fig.align='center', fig.height=4, fig.width=5, warning=FALSE, message=FALSE, fig.cap='Violence perpetrators in the Pinochet regime, 1973-1990'}
# Load requied packages
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
if (!require("lubridate")) {
        install.packages("lubridate")
}
# Plot
pinochet %>% 
  select(c(perpetrator_affiliation, start_date_monthly)) %>%
  mutate(Year = year(start_date_monthly)) %>%
  filter(!is.na(perpetrator_affiliation)) %>% 
  filter(!is.na(Year)) %>%
  filter(Year >= 1975) %>%
  group_by(perpetrator_affiliation, Year) %>%
  summarise(no_rows = length(perpetrator_affiliation)) %>%
  ggplot(aes(x = Year, y = no_rows, colour = perpetrator_affiliation)) +
  viridis::scale_color_viridis(discrete = TRUE,
                               end = 0.5, direction = -1) + 
  geom_line() +
  theme_minimal() +
  labs(x = NULL, y = NULL, title = "Violence Perpetrators", 
       subtitle = "Pinochet Regime, 1975-1990") +
  scale_x_continuous(breaks = c(1975, 1980, 1985, 1990)) +
  scale_y_continuous(breaks = c(0, 50, 100, 135)) + 
  facet_grid(perpetrator_affiliation ~ ., scales = "fixed") + 
  theme(legend.position = "bottom") + 
  theme(legend.title=element_blank())
```

### 2019-06-03 manuscript/online-appendix/online-appendix.Rmd
update R code manuscript

```{r sample-obs01, echo=FALSE, warning=FALSE, message=FALSE}
if (!require("kableExtra")) {
        install.packages("kableExtra")
}
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
load("/Users/politicaltheory/Documents/github/pinochet/data/pinochet.RData")

@@

```{r time-trend-perpetrators, fig.align='center', fig.height=4, fig.width=5, warning=FALSE, message=FALSE, fig.cap='Violence perpetrators in the Pinochet regime, 1973-1990'}
# Load requied packages
if (!require("tidyverse")) {
        install.packages("tidyverse")
}

# Plot
pinochet %>% 
  select(c(perpetrator_affiliation, start_date_monthly)) %>%
  mutate(Year = year(start_date_monthly)) %>%
  filter(!is.na(perpetrator_affiliation)) %>% 
  filter(!is.na(Year)) %>%
  filter(Year >= 1975) %>%
  group_by(perpetrator_affiliation, Year) %>%
  summarise(no_rows = length(perpetrator_affiliation)) %>%
  ggplot(aes(x = Year, y = no_rows, colour = perpetrator_affiliation)) +
  viridis::scale_color_viridis(discrete = TRUE, end = 0.5, direction = -1) + 
  geom_line() +
  theme_minimal() +
  labs(x = NULL, y = NULL, title = "Violence Perpetrators", 
       subtitle = "Pinochet Regime, 1975-1990") +
  scale_x_continuous(breaks = c(1975, 1980, 1985, 1990)) +
  facet_grid(perpetrator_affiliation ~ ., scales = "fixed") + 
  theme(legend.position = "bottom") + 
  theme(legend.title=element_blank())

>>>>

```{r sample-obs01, echo=FALSE, warning=FALSE, message=FALSE}
if (!require("kableExtra")) {
        install.packages("kableExtra")
}
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
if (!require("pinochet")) {
        install.packages("pinochet")
}

@@

```{r time-trend-perpetrators, fig.align='center', fig.height=4, fig.width=5, warning=FALSE, message=FALSE, fig.cap='Violence perpetrators in the Pinochet regime, 1973-1990'}
# Load requied packages
if (!require("tidyverse")) {
        install.packages("tidyverse")
}
if (!require("lubridate")) {
        install.packages("lubridate")
}

# Plot
pinochet %>% 
  select(c(perpetrator_affiliation, start_date_monthly)) %>%
  mutate(Year = year(start_date_monthly)) %>%
  filter(!is.na(perpetrator_affiliation)) %>% 
  filter(!is.na(Year)) %>%
  filter(Year >= 1975) %>%
  group_by(perpetrator_affiliation, Year) %>%
  summarise(no_rows = length(perpetrator_affiliation)) %>%
  ggplot(aes(x = Year, y = no_rows, colour = perpetrator_affiliation)) +
  viridis::scale_color_viridis(discrete = TRUE, end = 0.5, direction = -1) + 
  geom_line() +
  theme_minimal() +
  labs(x = NULL, y = NULL, title = "Violence Perpetrators", 
       subtitle = "Pinochet Regime, 1975-1990") +
  scale_x_continuous(breaks = c(1975, 1980, 1985, 1990)) +
  scale_y_continuous(breaks = c(0, 50, 100, 135)) + 
  facet_grid(perpetrator_affiliation ~ ., scales = "fixed") + 
  theme(legend.position = "bottom") + 
  theme(legend.title=element_blank())
